---
title: "`r if (nzchar(params$res$settings$title)) params$res$settings$title else 'Burden of disease report'`"
date: "`r format(params$res$settings$timestamp, '%d %B %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    theme: flatly
    self_contained: true
params:
  res: NULL
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE,
                      fig.width = 9, fig.height = 6, dpi = 110)
r <- params$res
s <- r$settings
cur <- s$currency
ci <- round(s$conf * 100)
tot <- function(m, f = "estimate") r$totals[r$totals$measure == m, f]
```

## Summary

The disease caused an estimated **`r format_num(tot("DALY"), 0)` DALYs**
(`r ci`% UI `r format_num(tot("DALY", "lower"), 0)`–`r format_num(tot("DALY", "upper"), 0)`),
equivalent to `r format_num(tot("DALY per 100,000"), 1)` DALYs per 100,000 population.
Years of life lost account for `r format_num(tot("YLL") / tot("DALY") * 100, 1)`% of the total.

The total economic burden was **`r format_money(tot("Total economic burden"), cur)`**
(`r ci`% UI `r format_money(tot("Total economic burden", "lower"), cur)`–`r format_money(tot("Total economic burden", "upper"), cur)`).

```{r totals}
knitr::kable(format_totals_table(r$totals, cur, s$conf), align = "lrrrr")
```

## By age and sex

```{r pyramid}
plot_daly_pyramid(r$by_stratum)
```

```{r uncertainty}
plot_measure_uncertainty(r$by_stratum, "DALY", s$conf)
```

```{r stratum-table}
wide <- r$by_stratum[r$by_stratum$measure %in% c("Deaths", "Cases", "YLL", "YLD", "DALY"), ]
tab <- reshape(wide[, c("age", "sex", "measure", "estimate")], idvar = c("age", "sex"),
               timevar = "measure", direction = "wide")
names(tab) <- sub("^estimate\\.", "", names(tab))
tab <- tab[order(tab$sex != "Males", tab$age), ]
tab$age <- age_group_labels(unique(r$by_stratum$age))[match(tab$age, sort(unique(r$by_stratum$age)))]
names(tab)[1:2] <- c("Age group", "Sex")
knitr::kable(tab, digits = c(0, 0, 0, 0, 1, 1, 1), row.names = FALSE,
             format.args = list(big.mark = ","))
```

## By health state

```{r states}
knitr::kable(format_state_table(r$by_state, s$conf), align = "llrrrr")
```

## Economic burden

Amounts in `r cur` (label only; no currency conversion applied).

```{r econ}
plot_economic_burden(r$totals, cur)
```

- Direct costs = cases × `r format_money(s$cost_per_case, cur, 2)` + deaths × `r format_money(s$cost_per_death, cur, 2)`
- Productivity loss = DALYs × GDP per capita (`r format_money(s$gdp_per_capita, cur, 2)`)

## Inputs and methods

```{r hs-inputs}
hs <- s$health_states
knitr::kable(data.frame(
  `Health state` = hs$health_state,
  `Disability weight` = sprintf("%.3f (%.3f–%.3f)", hs$dw_mean, hs$dw_lower, hs$dw_upper),
  Duration = sprintf("%s %s (%.4f years)", hs$duration, hs$duration_unit, hs$duration_years),
  check.names = FALSE))
```

- DALY = YLL + YLD. YLL = deaths × standard life expectancy at the average age of the age group's lower and upper bound, from the preloaded GBD reference life table (no discounting, no age weighting). YLD = cases × disability weight × duration (incidence-based).
- Uncertainty: `r format_num(s$n_iter)` Monte Carlo iterations (seed `r s$seed`). Disability weights drawn from PERT distributions (mode = mean, bounds = 95% CI); cases and deaths in each age-sex group drawn from Poisson distributions with the observed counts as means. The `r ci`% uncertainty interval is the 2.5th–97.5th percentile of the draws; the estimate column uses observed counts and mean disability weights.
- Total population: `r format_num(s$population_total)`.
